--- 
title: "Random Intercept Cross-Lagged Panel Model"
author: "-"
date: "Creado: 2021-03. Actualizado: `r Sys.Date()`"
knit: bookdown::render_book
site: bookdown::bookdown_site
documentclass: book
classoption: a4paper,12pt,twoside
lot: no
lof: no
link-citations: yes
bibliography: [book.bib, packages.bib]
biblio-style: apalike
colorlinks: yes
linktocpage: yes
linkcolor: black
urlcolor: blue
monofont: Source Code Pro
monofontoptions: Scale=0.7
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites {-}

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<p xmlns:dct="http://purl.org/dc/terms/" xmlns:cc="http://creativecommons.org/ns#"><a rel="cc:attributionURL" href="www.completar.com"><span rel="dct:title">Escuela de Invierno COES: Random Intercept Cross-Lagged Panel Model</span></a>, <a rel="cc:attributionURL" href="mailto:pjcarozzi@uc.cl"><span rel="cc:attributionName">[Completar Atribución]</span></a> esta bajo una licencia de Creative Commons <a href="https://creativecommons.org/licenses/by-nc-sa/4.0/deed.es">Atribución-NoComercial-CompartirIgual 4.0 Internacional</a> (CC BY-NC-SA 4.0) </p> <p align="center"><a href="https://creativecommons.org/licenses/by-nc-sa/4.0/deed.es"><img style="height:22px!important;margin-left: 3px;vertical-align:text-bottom;" src="https://search.creativecommons.org/static/img/cc_icon.svg" /><img  style="height:22px!important;margin-left: 3px;vertical-align:text-bottom;" src="https://search.creativecommons.org/static/img/cc-by_icon.svg" /><img  style="height:22px!important;margin-left: 3px;vertical-align:text-bottom;" src="https://search.creativecommons.org/static/img/cc-nc_icon.svg" /><img  style="height:22px!important;margin-left: 3px;vertical-align:text-bottom;" src="https://search.creativecommons.org/static/img/cc-sa_icon.svg" /></a></p>
